Deciding to Disclose

### 2015-06-02 Model.tex
Correct Bayes eg

Returning to our example agent, we now add slightly more information, and stipulate that they have in fact encountered a harshly judgemental midwife in all three rounds, hence \(n_{h}=3\). Their prior beliefs remain uninformative, i.e. \(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i}=1,i \in \{r,n\}\). As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -

\begin{equation*}
\begin{align*}
R_{w}(s_{w}, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, l, j)p(j)p(i | s_{w}),
R_{w}(s_{w}, l) &= 
\end{align}
\end{equation}

>>>>

Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\), and \(n_{l,n}=2\), \(n_{m,n}=1\). Their prior beliefs remain uninformative, i.e. \(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\). As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -

\begin{equation*}
\begin{align*}
R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) - u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} &= \frac{2}{3}\\
p(r | l) &= \frac{1 + 0}{1 + 1 + 2} &= \frac{1}{4}\\
p(n | l) &= \frac{1 + 2}{1 + 1 + 2} &= \frac{3}{4}\\
R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
R_{w}(l, l) &= -10
\end{align}
\end{equation}

and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-\frac{1}{2}\)) signals, once again concluding that honesty is the better option.
